---
title: "Exercise 2"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Data wrangling with dplyr

First load the `nycflights13` and `tidyverse` packages, and the flights data set.

```{r}
library(nycflights13)
library(tidyverse)

data(flights)
```

## Find all flights that

Had an arrival delay of two or more hours.

```{r}

```

Flew to Houston (IAH or HOU).

```{r}

```

Were operated by United, American, or Delta. Hint: You may need to look at the documentation for `airlines` and `flights`.

```{r}

```

Arrived more than two hours late but didn't leave late.

```{r}

```

## Grouped summaries

Which carrier had the worst average arrival delay?

```{r}

```

## Compute and compare variables [HARD]

Compare `dep_time`, `sched_dep_time`, and `dep_delay`. Are they consistent? Explain your findings. [HARD]

You might find the following function helpful:

```{r}
# Converts times in HHMM or HMM formats to minutes since midnight.
# Midnight is represented as 2400, which is 1440 minutes, so we also convert 1440 to 0.
time2mins = function(x) {
  (x %/% 100 * 60 + x %% 100) %% 1440
}

# %/% indicates integer division: 5 %/% 3 evaluates to 1
# %% indicates modulo or remainder: 5 %% 3 evaluates to 2
```

```{r}

```

Hint: think about flights that were scheduled to depart before midnight, but actually departed after midnight.
