---
title: "Exercise 4"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# R programming

## Vectors and lists

What does `mean(is.na(x))` tell you about a vector `x`? What about `sum(!is.finite(x))`?

Experiment with the following vector:

```{r}
x <- c(-Inf, -1, 0, 1, Inf, NA)

```

What happens when you subset with a positive integer that's bigger than the length of the vector? What happens when you subset with a name that doesn't exist?

```{r}

```


## Functions

Write a function that takes a vector argument and returns the elements at even numbered positions. Test your function.

```{r}

```

Write a function that takes a numeric vector and returns only even numbers (and no missing values). Test your function.

```{r}

```

## Iteration with purrr map functions

For this part, load the tidyverse package.

```{r}
library(tidyverse)
```

Use a map function to compute the mean of every column of `mtcars`.

```{r}

```

[Harder] Use a map function to compute the number of unique values in each column of the `iris` dataset.

Hint: you can pass a formula starting with ~ to the purrr map functions. Read the documentation for `purrr::map`.

```{r}

```

