---
title: "Exercise 1"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Data visualization with ggplot2

First load the `tidyverse` set of packages.

```{r}
library(tidyverse)
```

## First steps

Let's use the `mpg` dataset for the next few exercises.

How many rows are in `mpg`? How many columns?

```{r}
str(mpg)
```

What does the `drv` variable desribe? Read the help for `?mpg` to find out.

```{r}
?mpg
```

For reference here is the basic `ggplot2` template:

```{r, eval=FALSE}
ggplot(data = <DATA>) + 
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```

Use this template and the `mpg` dataset to plot `displ` vs `hwy`. Hint: Use the `geom_point` function.

```{r}

```

What do you think will happen when you run the following code?

```{r}
ggplot(data = mpg)
```

Make a scatterplot of `hwy` vs `cyl`. Note that `cyl` takes on only discrete integer values.

```{r}

```

What happens if you make a scatterplot of `class` vs `drv`? Why is the plot not useful?

```{r}

```

## Aesthetic mappings

What's wrong with the following code? Why are the points not blue?

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

Copy the code above to the following chunk. Can you fix it?

```{r}

```

Which variables in `mpg` are categorical? Which variables are continuous? (Hint: Type `?mpg` to read the documentation for the dataset.)

```{r}

```

Map a continous variable to `color`, `size`, and `shape`. How do these aesthetics behave differently for categorical versus continuous variables?

```{r}

```