---
title: "Exercise 2"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Data wrangling with dplyr

First load the `nycflights13` and `tidyverse` packages.

```{r}
library(nycflights13)
library(tidyverse)
```

## Find all flights that

Had an arrival delay of two or more hours.

```{r}

```

Flew to Houston (IAH or HOU).

```{r}

```

Were operated by United, American, or Delta. Hint: You may need to look at the documentation for `airlines` and `flights`.

```{r}

```

Arrived more than two hours late but didn't leave late.

```{r}

```

## Grouped summaries

Which carrier has the worst average arrival delay?

```{r}

```

## Add and compare variables [HARD]

Compare `air_time` with `arr_time - dep_time`. What do you expect to see? What do you see? What do you need to do to fix it?

Hint: You might find the following function useful:

```{r}
# converts times in HHMM or HMM format to minutes since midnight
time2mins <- function(x) {
  (x %/% 100 * 60 + x %% 100) %% (60 * 24)
}
```

For example, an `arr_time` of 1754 is 1074 minutes after midnight.

```{r}
arr_time <- 1754
time2mins(arr_time)
```

```{r}

```

Hint: Think about flights that depart before midnight and arrive after midnight.

Hint: What about flights with destinations in other time zones?

