---
title: "Exercise 3"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Exploratory data analysis

First load the `tidyverse` package.

```{r}
library(tidyverse)
```

## Visualizing distributions

Explore the distributions of each of the x, y, and z variables in `diamonds`. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.

```{r}

```

Explore the distribution of price. Do you discover anything unusual or surprising? (Hint: carefully think about the bin width and make sure you try a wide range of values.)

```{r}

```

How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference?

```{r}

```

## Covaration

What variable in the diamonds dataset is most important for predicting the price of a diamond? How is that variable correlated with cut? Why does the combination of those two relationships lead to lower quality diamonds being more expensive?

```{r}

```

Visualize the distribution of carat, partitioned by price.

```{r}

```

How does the price distribution of very large diamonds compare to small diamonds? Is it as you expect, or does it surprise you?

```{r}

```
